Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-28 paper/paper.tex
moved introductions to intro section and changed to subsections

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% documentclass was [sigconf]{acmart} changed to match with the given overleaf link

@@

@@

\section{Eye Tracking Introduction}
Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements. In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.

\section{QBTest Introduction}
The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy. Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.

\section{Typing Test Introduction}
Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success. However, various factors can influence typing efficiency, including environmental stimuli such as music. Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.

>>>>

\documentclass[manuscript, screen]{acmart} %removing review removes the numbers on left side
% documentclass was [sigconf]{acmart} changed to match with the given overleaf link

@@

\subsection{Eye Tracking}
Eye tracking technology, such as the EyeWriter 2.0, has become increasingly valuable in cognitive research, allowing for precise measurement and analysis of visual attention and eye movements. In this study, we incorporate the EyeWriter 2.0 to track participants' eye movements during the QBTest, a hand-eye coordination task.

\subsection{QBTest}
The Quantified Behavioral Test (QBTest) is a well-established tool for assessing cognitive function, particularly in measuring hand-eye coordination, speed, and accuracy. Developed as a standardized measure, the QBTest provides valuable insights into cognitive performance across different tasks and conditions.

\subsection{Typing Test}
Typing proficiency is a fundamental skill in today's digital age, essential for academic and professional success. However, various factors can influence typing efficiency, including environmental stimuli such as music. Understanding how music affects typing speed and accuracy is crucial for optimizing work and study environments.

@@
